---
title: "Getting Started with SankeyDiagramGenerator"
author: "Your Name"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with SankeyDiagramGenerator}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

The `SankeyDiagramGenerator` package provides tools to create interactive Sankey diagrams from your data. Sankey diagrams are useful for visualizing flows between different entities, such as energy flows, resource allocation, or process flows.

## Installation

You can install the package from source:

```{r, eval=FALSE}
# Install from local source
install.packages("path/to/SankeyDiagramGenerator", repos = NULL, type = "source")

# Or using devtools
devtools::install_local("path/to/SankeyDiagramGenerator")
```

## Basic Usage

### Creating a Simple Sankey Diagram

```{r, eval=FALSE}
library(SankeyDiagramGenerator)

# Create sample data
data <- data.frame(
  source = c("A", "A", "B", "B", "C"),
  target = c("B", "C", "D", "E", "E"),
  value = c(10, 5, 8, 3, 7)
)

# Create Sankey diagram
diagram <- create_sankey(data, title = "My Flow Diagram")
diagram
```

### Loading Data from CSV

```{r, eval=FALSE}
# Load data from a CSV file
csv_data <- load_data_from_csv("path/to/your/data.csv")

# Create diagram
diagram <- create_sankey(csv_data)
diagram
```

### Using Sample Data

The package includes sample datasets:

```{r, eval=FALSE}
# Get path to sample data
sample_file <- system.file("extdata", "sample_energy_flow.csv", 
                          package = "SankeyDiagramGenerator")

# Load and visualize
energy_data <- load_data_from_csv(sample_file)
energy_diagram <- create_sankey(energy_data, title = "Energy Flow")
energy_diagram
```

## Data Format

Your data should have three columns:

- `source`: The starting node of the flow
- `target`: The ending node of the flow
- `value`: The magnitude of the flow (numeric)

Example:

```
source,target,value
A,B,10
A,C,5
B,D,8
```

## Advanced Options

You can customize the appearance of your Sankey diagram:

```{r, eval=FALSE}
diagram <- create_sankey(
  data,
  title = "Custom Diagram",
  font_size = 14,
  node_width = 20
)
```

## Preparing Data Manually

If you need more control, you can prepare your data separately:

```{r, eval=FALSE}
# Prepare data
prepared <- prepare_sankey_data(data)

# Inspect the structure
str(prepared)

# Create diagram
diagram <- create_sankey(prepared)
```

## Conclusion

The `SankeyDiagramGenerator` package makes it easy to create beautiful, interactive Sankey diagrams from your data. Experiment with different datasets and customization options to create the perfect visualization for your needs.
